---
title: "script_data_h_final"
author: "Raquel"
date: "2023-03-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries 

```{r cars}
library(xml2)
library(httr)
library(tidyverse)
library(sf)
library(rnaturalearth)
library(magrittr)
library(readr)
library(stringi)
library(mapSpain)
library(ggplot2)

```

# User agent

```{r}
# set_config(
#   user_agent(
#HERE, set your USER AGENT, you can check it in google
#   )
# )
```

# URLs

```{r}
url_priv <- "https://www.inforesidencias.com/centros/buscador/centros-de-dia-para-mayores/madrid/madrid/madrid"

url_publ <- "https://www.comunidad.madrid/servicios/asuntos-sociales/centros-mayores"


priv_raw <-  read_html(url_priv) 

publ_raw <-  read_html(url_publ) 
```

# Create Private dataframe

Get a group of every url with the addresses of the centers

```{r}
x <- "https://www.inforesidencias.com/centros/buscador/centros-de-dia-para-mayores/madrid/madrid/madrid?page=2"
url_group <- c(x, x, x, x, x, x, x, x, x, x, x, x, x, x)
url_group <- str_remove(url_group, pattern = "2")
url_group <- paste0(url_group, c(2:15))
url_group <- c(url_priv, url_group)
url_group
```

Extract the address of every url link.

```{r}

address_vector <- c(url_priv)
extract_address <- function(x) {
  Sys.sleep(5)
html_priv <-  read_html(x) %>% xml_child()
y <- html_priv %>% 
  xml_find_all("//address") %>% 
  xml_text()
}

private_dayc <- map(url_group, extract_address)
private_dayc

```

Transform into a dataframe

```{r}
df_priv <- as.data.frame(private_dayc)

df_priv <- data.frame(newcol = c(t(df_priv)), stringsAsFactors=FALSE)

```

Clean to standardize

```{r}
cdf_priv <- df_priv %>% 
  transmute(ADDRESS = toupper(newcol)) %>% 
  mutate(ADDRESS = str_remove(ADDRESS, "\n ")) %>% 
  mutate(ADDRESS = str_remove(ADDRESS, "C/")) %>% 
  mutate(ADDRESS = str_remove(ADDRESS, "\\.")) %>% 
  # remove street class
  mutate(ADDRESS = str_remove(ADDRESS, "CALLE|PLAZA|AVDA.|AV |AVENIDA|PASEO|BULV|GLORIETA DE LOS|PASEO DE LA|CTRA.|CTRA DE|CTRA. DE")) %>% 
  # remove postal code
  mutate(ADDRESS = str_remove(ADDRESS, "\\d\\d\\d\\d\\d")) %>% 
  # remove city info
  mutate(ADDRESS = str_extract(ADDRESS, ".+\\d+|.+S/N|.+,")) %>% 
  # Number column, Address name column, is private? column (PRIV)
  transmute(NUMBER = str_extract(ADDRESS, "\\d+"),
         NOMBRE = str_remove(ADDRESS, "\\d+")) %>% 
  mutate(NOMBRE = str_remove(NOMBRE, " NO"),
         NOMBRE = str_remove(NOMBRE, ",|S/N"),
         PRIV = 1) %>% 
  mutate(NOMBRE = str_remove_all(NOMBRE, "\\.")) %>% 
  mutate(NOMBRE = str_remove(NOMBRE, "-\\d+")) %>% 
  mutate(NOMBRE = str_remove(NOMBRE, "\\(.+")) %>% 
  mutate(NOMBRE = str_remove(NOMBRE, ",")) %>% 
  mutate(NOMBRE = str_remove(NOMBRE, "Nº")) %>% 
  mutate(NOMBRE = str_remove(NOMBRE, " 3 5 Y 6")) %>% 
  mutate(NOMBRE = str_remove(NOMBRE, "LCAL")) %>% 
  mutate(NOMBRE = str_replace(NOMBRE, "DE LA DIRECCIÓN", "DIRECCIÓN")) %>% 
  mutate(NOMBRE = str_replace(NOMBRE, "DE VILLAVERDE A", "VILLAVERDE A")) %>% 
  mutate(NOMBRE = str_replace(NOMBRE, "LA ISLA DE CUBA", "ISLA DE CUBA")) %>% 
  mutate(NOMBRE = str_replace(NOMBRE, "ISLA DE LA", "ISLA DE")) %>% 
  mutate(NOMBRE = str_replace(NOMBRE, "DE TALLERES", "TALLERES"))%>% 
  mutate(NOMBRE = str_replace(NOMBRE, "DE TALLERES", "TALLERES"))%>% 
  mutate(NOMBRE = str_replace(NOMBRE, "DE PORTUGAL", "PORTUGAL"))%>% 
  mutate(NOMBRE = str_replace(NOMBRE, "DE LA HABANA", "LA HABANA"))%>% 
  mutate(NOMBRE = str_replace(NOMBRE, "DE CANILLAS", "CANILLAS"))%>% 
  mutate(NOMBRE = str_replace(NOMBRE, "DE PALAFOX", "PALAFOX"))%>% 
  mutate(NOMBRE = str_replace(NOMBRE, "DE CÓRDOBA", "CÓRDOBA"))%>%
  mutate(NOMBRE = str_replace(NOMBRE, "ADE SAINZ", "ALCALDE SAINZ"))%>%
  mutate(NOMBRE = str_replace(NOMBRE, "CÁRMENES", "LOS CÁRMENES"))%>%
  mutate(NOMBRE = str_replace(NOMBRE, "PEÑASCALES", "LOS PEÑASCALES"))%>%
  mutate(NOMBRE = str_replace(NOMBRE, "JOSÉ JIMÉNEZ", "JOSÉ JIMÉNEZ MARTÍN"))%>%
  mutate(NOMBRE = str_remove(NOMBRE, "TRAVESERA "))%>%
  mutate(NOMBRE = str_replace(NOMBRE, " SRA ", " SEÑORA ")) %>% 
  mutate(NOMBRE = str_replace(NOMBRE, "GRAL", "GENERAL")) %>% 
  mutate(NOMBRE = str_replace(NOMBRE, "PÉREZ AYALA", "PÉREZ DE AYALA")) %>% 
  mutate(NOMBRE = str_replace(NOMBRE, "DR", "DOCTOR")) %>% 
  mutate(NOMBRE = str_squish(NOMBRE))  %>% 
  mutate(NUMBER = replace_na(NUMBER, "2")) %>% 
  mutate(NOMBRE = stri_trans_general(NOMBRE,"Latin-ASCII"))


cdf_priv
```

# Create Public dataframe

Get the public centers URLs

```{r pressure}

mainurl <- "https://www.comunidad.madrid/"#all senior day care center webpages where the direction info is, starts with this main url

url_publ <- publ_raw  %>%
  xml_find_all("//h3/a[@href ]")%>% xml_attr(attr = "href")
#to avoid the vector elements that are not the end of links 
url_publ <- url_publ[4:35]

#a loop to paste the beginning of the link stored as main url to the different ends of the link stored in url_publ
for (i in 1:length(url_publ)) {
  url_publ[i] <- paste0(mainurl, url_publ[i])
}

url_publ

```

 Extract public daycare centers addresses

```{r}

function_name <- function(x, y){ 
  Sys.sleep(5)
  x <- read_html(x)
  y <- x %>% xml_find_all("//span[@property = 'schema:streetAddress']//p")%>% xml_text()
  print(y)}

# Loop for the 32 urls
results_list <- list()

for (i in seq_along(url_publ)) {
  url <- url_publ[i]
  result <- function_name(url)
  results_list[[i]] <- result
}

print(results_list)

```

Transform the results to data frame

```{r}

df_publ <- as.data.frame(results_list)

df_publ <- data.frame(newcol = c(t(df_publ)), stringsAsFactors=FALSE)

df_publ <- head(df_publ, 32)
```

Clean dataframe: Street name & Number in different columns

```{r}
# Change to capital letters to fit el callejero dataframe

df_publ <- df_publ%>% mutate(newcol=toupper(newcol))

#Separate a 'Clase' column with Calle, Avenida... information to match El Callejero 

df_publ <- df_publ %>% 
  mutate(CLASE = str_extract(df_publ$newcol, "^[A-Z]+(?=\\s)|C/|AVDA."))%>%
  mutate(CLASE = str_replace(CLASE, "C/", "CALLE"))%>%#para que coincida con el callejero
  mutate(CLASE=str_replace(CLASE, "AVDA.", "AVENIDA"))#para que coincida con el callejero

#Separete the street name

df_publ <- df_publ %>% 
  #Regular expression: select every text since first blank space till fisrt coma
  mutate(NOMBRE = str_extract(df_publ$newcol, "(?<=\\s)[^,]+"))
  #Regular expression: remove la, las, de... from the street to fit El Callejero
 df_publ <- df_publ %>% 
   mutate(NOMBRE = gsub("^DE LAS|^DE LA|^DEL|^DE LOS","",NOMBRE))
         
  
```

Separete the number or s/n in another column

```{r}


df_publ <- df_publ %>% 
  mutate(NUMERO_TX = str_extract(df_publ$newcol, "\\d+|S/N"))%>%
  mutate(NUMERO_TX=str_replace(NUMERO_TX, "S/N", "1"))#in order to match El Callejero, we have changed s/n to 1, because we have guessed it is the number that most probably appears on a street

```


Create PRIV column to differenciate, between private center 1 and public center 0 
```{r}
df_publ <- df_publ %>% 
  mutate(PRIV = 0)#all publics, all 0
```

Modify df_publ dataframe in order for its columns to match El Callejero colums when merged

```{r}
df_publ<- df_publ%>% 
  mutate(NUMERO_TX=as.character(NUMERO_TX))%>%
  mutate(NOMBRE= str_replace_all(NOMBRE, "SANTA JOAQUINA VEDRUNA",
                             "SANTA JOAQUÍNA DE VEDRUNA"))%>%
 mutate(NOMBRE= str_replace_all(NOMBRE, "CARMENES",
                             "LOS CÁRMENES"))%>%
   mutate(NOMBRE= str_replace_all(NOMBRE, "BENIMANET",
                             "BENIMAMET"))%>%
  mutate(NOMBRE= str_replace_all(NOMBRE, "SIERRA PALOMERAS",
                             "SIERRA DE PALOMERAS"))


```

Load street data of Madrid from "El Callejero"
Source: https://datos.madrid.es/portal/site/egob/menuitem.c05c1f754a33a9fbe4b2e4b284f1a5a0/?vgnextoid=b3c41f3cf6a6c410VgnVCM2000000c205a0aRCRD&vgnextchannel=374512b9ace9f310VgnVCM100000171f5a0aRCRD&vgnextfmt=default

```{r}
callejero <- read.csv("../datasets/Direcciones_vigentes2016.csv", 
                      sep = ";",
                      fileEncoding = "ISO-8859-1") %>% 
  select(CLASE, NOMBRE, NUMERO_TX, starts_with("UTM"))

cdf <- callejero %>%
  mutate(NUMBER = NUMERO_TX) %>% 
  mutate(NOMBRE = stri_trans_general(NOMBRE,"Latin-ASCII")) %>% 
  full_join(cdf_priv, by = c("NUMBER", "NOMBRE")) %>% 
  drop_na(PRIV) %>% 
  select(-NUMERO_TX)

cdf <- cdf[!duplicated(cdf$NOMBRE), ] 

cdf

```

 Join df_publ dataframe to El Callejero
 
```{r}

df_publ_plot  <- df_publ%>%full_join(callejero, by= c("NOMBRE", "CLASE", "NUMERO_TX")) %>%
  drop_na(PRIV)

```

Ciudad vs Comunidad Autónoma

The scrapped webpage had all senior day care centers from Comunidad de Madrid, not from Madrid city, out of 32 centers, 13 centers are inside Comunidad de Madrid but they are not in Madrid city, therefore Madrid city only has 19 senior public day care centers

```{r}
#calle damas no está en madrid ciudad es Alcalá de Henares --ROW1
#Plaza Orense en Fuenlabrada-- ROW 2
#Avenida d elas naciones. Gracai Fuenlabrada --ROW 9
#	AVDA. DE LAS CIUDADES, NÚM. 31 en Getafe-- ROW 10
#AVENIDA DE LA MANCHA, NÚM. 33 Leganés-- ROW 11
#	AVENIDA DEL MAR MEDITERRÁNEO, 16 Leganés-- ROW 12
#CALLE RÍO JARAMA, S/N Leganés-- ROW 14
#CALLE CORONADOS, NÚM. 7 Pinto-- ROW 17
#CALLE GOBERNADOR, NÚM. 80 Aranjuez-- ROW 20
#CALLE PADRE BLANCO, S/N C/V FERROCARRIL Getafe-- ROW 21
#	CALLE PILAR, NÚM. 6 --ROW 27
# SECTOR DESCUBRIDORES, NÚM. 24 Tres Cantos-- ROW 29
#	CALLE MORALES ANTUÑANO, NÚM. 9 Collado Villalba-- ROW 32

df_publ_plot  <- df_publ_plot [-c(1, 2, 9, 10, 11, 12, 14, 17, 20, 21, 27, 29, 32),]

#Camarena and Humanes have duplicated rows, so we erased them in order to have jsut one row

df_publ_plot  <- df_publ_plot [-c(3, 5, 9),]

df_publ_plot

```

# Join private & public

```{r}
#Modify to join 
df_priv_plot <- cdf %>% 
  rename(NUMERO_TX = NUMBER) %>% 
  mutate(PRIV = NA)#To avoid picturing public ones as private ones

#Modify to join 
df_publ_plot <- df_publ_plot%>% select(-newcol)

#Join both
df_plot <- rbind(df_publ_plot, df_priv_plot)

#Somo private observations (PRIV=NA) are actually public observations (PRIV=0)
df_plot <- df_plot [!duplicated(df_plot $NOMBRE), ]

df_plot$PRIV <- df_plot$PRIV %>% replace(is.na(.), 1)
```

# Plotting results

## Madrid map

Prepare dataframe to plot a map remove , to put .
 
```{r}
# to drop the observations that cannot be plotted
df_plot <- df_plot %>%  drop_na(UTMX_ETRS, UTMY_ETRS)%>%
  mutate(UTMX_ETRS= str_replace(UTMX_ETRS, ",", "."), #to be able to transform it to                                                       numeric
         UTMY_ETRS= str_replace(UTMY_ETRS, ",", "."))%>%
  mutate(UTMX_ETRS= as.numeric(UTMX_ETRS),
         UTMY_ETRS= as.numeric(UTMY_ETRS))#Transforming to numeric type to be able to work with them and sf functions

#SAVE IT

write.csv(cdf, file = "../datasets/df_plot")
```

Loading Madrid map

```{r}
Madrid <- esp_get_munic(munic = "Madrid", epsg = "4326") %>%
  filter(cmun == "079") %>% 
  # Standardizing labels
  mutate(
    Municipio = esp_dict_translate(name, "es")
  )

```

Transforming longitude and latitude to sf in order to plot it

```{r}
df_plot  <- df_plot %>% drop_na(c(UTMX_ETRS, UTMY_ETRS))
df_plot_sf <- st_as_sf(df_plot, coords = c("UTMX_ETRS", "UTMY_ETRS"), crs = 25830)

# transform the spatial data frame into the appropriate CRS for mapspain
df_plot_sf <- st_transform(df_plot_sf, crs = st_crs(Madrid))

```

Map plot of senior day care centers in Madrid

```{r}
ggplot() +
  geom_sf(data = Madrid) +
  geom_sf(data = df_plot_sf, aes(color = ifelse(PRIV == "0", "Public center", "Private center")), size = 1) +
  scale_color_manual(name= "Senior day care center type", values = c("Public center" = "green", "Private center" = "red")) +
  ggtitle("Location of senior day care centers in Madrid city")+
  theme_minimal()+
    theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
```


## Bar plots

Load El Callejero with the district numbers to merge it

```{r}
callejero2 <- read.csv("../datasets/Direcciones_vigentes2016.csv", 
                      sep = ";",
                      fileEncoding = "ISO-8859-1") %>% 
  select(NOMBRE, DISTRITO) %>% distinct(NOMBRE, .keep_all= TRUE) %>% 
  mutate(NOMBRE = stri_trans_general(NOMBRE, "Latin-ASCII"))

df_plot2 <- df_plot%>% 
  mutate(NOMBRE = stri_trans_general(NOMBRE, "Latin-ASCII"))
df_plot2 <- df_plot2 %>% left_join(callejero2, by = "NOMBRE") 


```

Data cleaning

```{r}
# Tweak the dataframe to plot
df_barplot <- df_plot2 %>% select(DISTRITO, PRIV, NOMBRE) %>% group_by(DISTRITO) %>% 
  summarise(
  n_centers = n_distinct(NOMBRE),
  n_PRIV = sum(PRIV == 1),
  n_PUBL = sum(PRIV != 1)) %>% 
  mutate(`COD-DISTRITO` = DISTRITO) %>% 
  select(-DISTRITO)

# merge with district names
df_parks <- read_csv2(file = "../datasets/parques-jardines-Ayto de Madrid_2023.csv") # List of parks and gardens from Ayto. de Madrid
DISTRICT_NUM_Madrid <- df_parks %>% 
  # select variables
  select(DISTRITO, `COD-DISTRITO`) %>%
  unique() %>% drop_na() %>% 
  # introduce 'Ñ's, as they are not readen correctly 
  mutate(DISTRITO = str_replace_all(DISTRITO, "\xd1", "Ñ")) 

# add district names
cdf_barplot <- df_barplot %>% 
  left_join(DISTRICT_NUM_Madrid, 
            by = "COD-DISTRITO")

```

Bar plots

```{r}
### Individual barplots
## total n_centers
barplot_total <- cdf_barplot %>%
  arrange(desc(n_centers)) %>% # sort rows by n_centers in descending order
  mutate(DISTRITO = fct_reorder(DISTRITO, n_centers, .desc = TRUE)) %>% 
  ggplot(aes(x = DISTRITO, y = n_centers)) +
  geom_segment(aes(x = DISTRITO, y = 0, xend = DISTRITO, yend = n_centers), color = "darkviolet", size = 2) +
  coord_flip() +
  labs(x = "", y = "Senior day care centers per district in Madrid", color = "")
## private n_centers (cambiar)
barplot_priv <- cdf_barplot %>%
  arrange(desc(n_PRIV)) %>% # sort rows by n_centers in descending order
  mutate(DISTRITO = fct_reorder(DISTRITO, n_PRIV, .desc = TRUE)) %>% 
  ggplot(aes(x = DISTRITO, y = n_PRIV)) +
  geom_segment(aes(x = DISTRITO, y = 0, xend = DISTRITO, yend = n_PRIV), color = "darkred", size = 2) +
  coord_flip() +
  labs(x = "", y = "Private senior day care centers per district in Madrid", color = "")
## public n_centers (cambiar)
barplot_publ <- cdf_barplot %>%
  arrange(desc(n_PUBL)) %>% # sort rows by n_centers in descending order
  mutate(DISTRITO = fct_reorder(DISTRITO, n_PUBL, .desc = TRUE)) %>% 
  ggplot(aes(x = DISTRITO, y = n_PUBL)) +
  geom_segment(aes(x = DISTRITO, y = 0, xend = DISTRITO, yend = n_PUBL), color = "lightgreen", size = 2) +
  coord_flip() +
  labs(x = "", y = "Public senior day care centers per district in Madrid", color = "")  

barplot_total
barplot_priv
barplot_publ
```

```{r}
# bar plot
cdf_barplot %>%
  arrange(desc(n_centers)) %>% # sort rows by n_centers in descending order
  mutate(DISTRITO = fct_reorder(DISTRITO, n_centers, .desc = TRUE)) %>%
  ggplot(aes(x = DISTRITO)) +
  geom_col(aes(y = n_centers, fill = "Private centers"), width = 0.5) +
  geom_col(aes(y = n_PUBL, fill = "Public centers"), width = 0.5) +
  scale_fill_manual(values = c("Public centers" = "lightgreen", "Private centers" = "darkred")) +
  labs(fill = "") +
  labs(x = "", y = "Number of day care centers", color = "")  +
  labs(title = "Public and Private senior day care centers per district, Madrid") +
  scale_y_continuous(n.breaks = 13) +
  coord_flip() 
```


